Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
conclusiones

From the purely numerical point of view, a better understading of the
influence of baryons on the different properties we have measure  will
certainly require to study how the halo and the disc co-evolved as a
function of time. 
\cite{VeraCiro11} advanced suggested the idea that the current dark
matter halo shape strongly correlates with the time evolution of the
halo as traced by the shape measured at the virial radius.
The opposed trend of triaxiality as a functio of radius between the
MHD and the DMO simulations, together with twsiting effect in some of
the halos seems to suggest that this effect might no longer hold.

Calibrating the effect of the cosmic web (both dark matter and gaseous)
\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
could also be required to gain a full picture of this behaviour.

From the results presented in this work we advance the idea that the
twisting shells in the density is a feature that deserves to be
explored in the process of constraining shape parameters from tidal
stream data. 
The inclusion of a parameterization describing this degree of
twisting might relax the conflict between the observational
constraints and the numerical results.

>>>>

Using dark matter only simulations \cite{VeraCiro11} suggested that
the current dark matter halo shape strongly correlates with the time
evolution of the halo as traced by the shape measured at the virial radius. 
This effect might no longer hold once baryons are included. 
The opposed trend of triaxiality in MHD simulation as a function of
radius to the DMO simulations together with the twisting effect in some of 
the halos seems to suggest that that historical buildup memory is not
stored in the halo at $z=0$.

A more complete understading of the influence of baryons on the
different properties we have measure will certainly require to study
how the halo and the disc co-evolved as a function of time and a
calibrating the effect of the cosmic web (both dark matter and
gaseous)  \citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
We finalize by suggesting that twisting shells in the density is a
feature that deserves to be explored in the process of constraining
shape parameters from tidal stream data.  The inclusion of a
parameterization describing this degree of twisting might relax the
conflict between the observational constraints and the numerical
results.
